Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-03 infuse/system.tex
restructure
restructuring
fix figures and some citations

\begin{figure}[ht]
\centering
\hspace*{0.02\linewidth}%
\includegraphics[width=\linewidth]{infuse/glyph-key}
\caption{
(a) The glyph representation of a feature in the \infuse system.
(b) Multiple models for each feature are represented as \emph{model sections}.  In this example, the feature is divided into four sections, as it was ranked by four feature selection algorithms (Information Gain, Fisher-Score, Relative Risk, and Odds Ratio.).
(c) Each section is further divided into \emph{fold slices} representing each of the cross-validation folds. Each fold slices features a inward-filling bar that represents the rank of this feature in that fold.
A longer bar implies the feature has a better rank.  If no bar appears, the feature was unranked in the fold, and thus did not meet the importance threshold.
\vspace*{2em}
}
\label{fig:glyph-key}
\end{figure}

\begin{figure}[ht]
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g0}
\caption{}
\label{subfig:inward}
\end{subfigure}%
\hspace*{0.01\linewidth}%
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g1}
\caption{}
\label{subfig:pie}
\end{subfigure}%
\hspace*{0.01\linewidth}%
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g2}
\caption{}
\label{subfig:star}
\end{subfigure}%
\hspace*{0.01\linewidth}%
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g3}
\caption{}
\label{subfig:matrix}
\end{subfigure}%
\caption{
Different glyph designs.
\subref{subfig:inward} shows \emph{fold slices} with bars growing from perimeter to center
whereas \subref{subfig:pie} grows from center to perimeter.
\subref{subfig:star} shows a typical starburst glyph and
\subref{subfig:matrix} shows a matrix using luminance to show the ranks.
Note that in \subref{subfig:pie} and \subref{subfig:star} it is difficult
to see that this feature is unranked in the third fold from the right in
the top left quadrant.
The values in \subref{subfig:star} are difficult to read because
there is no reference to how big the values are.
Luminance, as used in \subref{subfig:matrix} is a harder perceptual attribute for users
to interpret and distinguish than length and area are, as used by the other glyphs.
}
\label{fig:glyph_design}
\end{figure}

@@

\begin{figure*}[ht]
\centering
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/ap}
\label{subfig:ap}
\end{subfigure}%
~%
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/mi}
\label{subfig:mi}
\end{subfigure}%
~%
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/ba}
\label{subfig:ba}
\end{subfigure}%
~%
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/si}
\label{subfig:si}
\end{subfigure}
\caption{
Different axis combinations for the scatter-plot layout.
In \subref{subfig:ap} the average rank is plotted against the pick count.
Most of the features appear in the lower half because features are rarely picked by more than two algorithms in this example.  The bottom-right shows features that are only chosen
by two models but were ranked very high by them.
\subref{subfig:mi} shows the median rank plotted against the importance.
Notice that the plot looks similar to \subref{subfig:ap} since importance
is a combination of the axes from \subref{subfig:ap}.
The axes in \subref{subfig:ba} are best rank versus average rank.
Features can only appear below the diagonal.
The standard deviation of the ranks is plotted against the importance
in \subref{subfig:si}.
The peak to the bottom right corner consists of features that are rarely
picked and therefore have lower variance.
The peak to the top right consists of features that
are consistently high ranked.
}
\label{fig:scatter}
\end{figure*}

@@

\vspace*{1em}
\subsubsection{Ranked Layout}\label{sec:rankedlayout}
The first layout available to users is the ranked layout, which arranges glyphs by their feature type, and sorts them by their overall importance.  The name of the feature type is shown at the first position in the group, after that the features are laid out row-first in a grid-like manner, as shown in Figure \ref{fig:system}. This space-filling approach results in features that are always visible without overlaps.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{infuse/classifier}
\caption{The Classifier View displays the results of the classification algorithms for all models.
Rows represent feature selection algorithms and columns represent classification algorithms.
A more detailed description of the cells can be
seen in Figure~\ref{fig:classifier-cell}.
The currently selected model is highlighted in orange, and the results for the same fold in different
feature selection algorithms are highlighted in yellow.  When users select a model, the features that make up the model are highlighted in the Feature and List views.
}
\label{fig:classifier}
\end{figure}

\begin{figure}[b]
\centering
\includegraphics[width=0.5\linewidth]{infuse/classifier-cell}
\caption{
Each cell in the Classifier View represents the scores of a particular model by a particular classifier.
On the left, there is a bar for each of the validation folds.  The height of each bar corresponds to the AUC score for each fold.  Immediately to the right of the fold bars, the thicker and darker bar and its height represents the average value across all folds.  This bar also features an error bar depicting the standard deviation across the folds.  Finally, to the right of the bars, there is a numerical representation of the average AUC score.}
\label{fig:classifier-cell}
\end{figure}

@@

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{infuse/selection}
\caption{
\infuse's Interactive Model Builder allows users to select sets of features and measure its quality.
Selected feature glyphs are highlighted by saturating their color.  The List View is sorted to show the selected features by their importance.  After a user has made their selections, they can evaluate their model by clicking the ``Evaluate Model" button.  This adds a new blue row to the the Classifier View, showing the results of the evaluation for the user-defined model.
}
\label{fig:selection}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\hspace*{0.02\linewidth}%
\includegraphics[width=0.95\linewidth]{infuse/glyph-key}
\caption[How to read the glyph representation of \infuse.]{
(a) The glyph representation of a feature in the \infuse system.
(b) Multiple models for each feature are represented as \emph{model sections}.  In this example, the feature is divided into four sections, as it was ranked by four feature selection algorithms (Information Gain, Fisher-Score, Relative Risk, and Odds Ratio.).
(c) Each section is further divided into \emph{fold slices} representing each of the cross-validation folds. Each fold slices features a inward-filling bar that represents the rank of this feature in that fold.
A longer bar implies the feature has a better rank.  If no bar appears, the feature was unranked in the fold, and thus did not meet the importance threshold.
}
\label{fig:glyph-key}
\end{figure}

\begin{figure}[t]
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g0}
\caption{}
\label{subfig:inward}
\end{subfigure}%
\hspace*{0.01\linewidth}%
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g1}
\caption{}
\label{subfig:pie}
\end{subfigure}%
\hspace*{0.01\linewidth}%
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g2}
\caption{}
\label{subfig:star}
\end{subfigure}%
\hspace*{0.01\linewidth}%
\begin{subfigure}{0.23\linewidth}
\centering
\includegraphics[width=\linewidth,clip,trim={2.4cm 4cm 1.7cm 4cm}]{infuse/g3}
\caption{}
\label{subfig:matrix}
\end{subfigure}%
\caption[Different glyph designs.]{
Different glyph designs.
\subref{subfig:inward} shows \emph{fold slices} with bars growing from perimeter to center
whereas \subref{subfig:pie} grows from center to perimeter.
\subref{subfig:star} shows a typical starburst glyph and
\subref{subfig:matrix} shows a matrix using luminance to show the ranks.
Note that in \subref{subfig:pie} and \subref{subfig:star} it is difficult
to see that this feature is unranked in the third fold from the right in
the top left quadrant.
The values in \subref{subfig:star} are difficult to read because
there is no reference to how big the values are.
Luminance, as used in \subref{subfig:matrix} is a harder perceptual attribute for users
to interpret and distinguish than length and area are, as used by the other glyphs.
}
\label{fig:glyph_design}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/ap}
\label{subfig:ap}
\end{subfigure}%
~%
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/mi}
\label{subfig:mi}
\end{subfigure}%
~%
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/ba}
\label{subfig:ba}
\end{subfigure}%
~%
\begin{subfigure}{0.24\linewidth}
\includegraphics[width=\linewidth]{infuse/si}
\label{subfig:si}
\end{subfigure}
\caption[Different axis combinations for the scatter-plot layout.]{
Different axis combinations for the scatter-plot layout.
In \subref{subfig:ap} the average rank is plotted against the pick count.
Most of the features appear in the lower half because features are rarely picked by more than two algorithms in this example.  The bottom-right shows features that are only chosen
by two models but were ranked very high by them.
\subref{subfig:mi} shows the median rank plotted against the importance.
Notice that the plot looks similar to \subref{subfig:ap} since importance
is a combination of the axes from \subref{subfig:ap}.
The axes in \subref{subfig:ba} are best rank versus average rank.
Features can only appear below the diagonal.
The standard deviation of the ranks is plotted against the importance
in \subref{subfig:si}.
The peak to the bottom right corner consists of features that are rarely
picked and therefore have lower variance.
The peak to the top right consists of features that
are consistently high ranked.
}
\label{fig:scatter}
\end{figure}

@@

\subsubsection{Ranked Layout}\label{sec:rankedlayout}
The first layout available to users is the ranked layout, which arranges glyphs by their feature type, and sorts them by their overall importance.  The name of the feature type is shown at the first position in the group, after that the features are laid out row-first in a grid-like manner, as shown in Figure \ref{fig:system}. This space-filling approach results in features that are always visible without overlaps.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\linewidth]{infuse/classifier}
\caption[The Classifier View.]{The Classifier View displays the results of the classification algorithms for all models.
Rows represent feature selection algorithms and columns represent classification algorithms.
A more detailed description of the cells can be
seen in Figure~\ref{fig:classifier-cell}.
The currently selected model is highlighted in orange, and the results for the same fold in different
feature selection algorithms are highlighted in yellow.  When users select a model, the features that make up the model are highlighted in the Feature and List views.
}
\label{fig:classifier}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.4\linewidth]{infuse/classifier-cell}
\caption[A cell of the Classifier View.]{
Each cell in the Classifier View represents the scores of a particular model by a particular classifier.
On the left, there is a bar for each of the validation folds.  The height of each bar corresponds to the AUC score for each fold.  Immediately to the right of the fold bars, the thicker and darker bar and its height represents the average value across all folds.  This bar also features an error bar depicting the standard deviation across the folds.  Finally, to the right of the bars, there is a numerical representation of the average AUC score.}
\label{fig:classifier-cell}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{infuse/selection}
\caption[\infuse's Interactive Model Builder.]{
\infuse's Interactive Model Builder allows users to select sets of features and measure its quality.
Selected feature glyphs are highlighted by saturating their color.  The List View is sorted to show the selected features by their importance.  After a user has made their selections, they can evaluate their model by clicking the ``Evaluate Model" button.  This adds a new blue row to the the Classifier View, showing the results of the evaluation for the user-defined model.
}
\label{fig:selection}
\end{figure}

### 2018-04-03 infuse/use_case.tex
fix figures and some citations

\begin{figure*}[ht]
\centering
\resizebox{0.9\linewidth}{!}{%
\begin{tikzpicture}
\newcommand*{\imgwidth}{3.7cm}
\newcommand*{\boxsize}{0.437cm}
\newcommand*{\boxpos}{(.295, -.18)}
\newcommand*{\rightimagepos}{(4.8, 0)}
\newcommand*{\leftimagepos}{(0, 0)}
\node[inner sep=0pt] at \leftimagepos
    {\includegraphics[width=\imgwidth]{infuse/ap}};
\node[inner sep=0pt] at \leftimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/ap}}};
\node[inner sep=2.5pt,very thick, text height=\boxsize] (zoom)
at \boxpos
    {\hspace*{\boxsize}};
\node[inner sep=-0.05pt] (lasso) at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\draw (zoom.north west) -- (lasso.north west);
\draw (zoom.south west) -- (lasso.south west);
\draw (zoom.north east) -- (lasso.north east);
\draw (zoom.south east) -- (lasso.south east);
\node[very thick, draw=red!90, text height=\boxsize]
at \boxpos {\hspace*{\boxsize}};
\node[inner sep=0pt, very thick] at \rightimagepos
    {\includegraphics[width=\imgwidth]{infuse/lasso}};
\node[inner sep=0pt, very thick, draw=red!90] at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\end{tikzpicture}%
}
\caption{
The scatterplot view allows users to compare multiple types of rankings.  In the case study, users became curious of the medication features that were chosen by only half of the models.  When reviewing these medications with domain experts, it became clear that features picked by the upper-half algorithms were as clinically significant as those picked by the bottom-half.  This indicates that merging results from feature selection algorithms makes sense for this predictive model.
}
\label{fig:usecase2}
\end{figure*}

\subsection{Insight 1: Data issues}
When the clinical researchers learned of \infuse's capabilities
to compare multiple feature selection algorithms, they decided to
expand their pipeline's feature selection algorithms from 2 to 4.
The team has used Information Gain and Fisher Score extensively
in prior work, and typically uses these same techniques due
to their familiarity and past success.
Nonetheless, the diabetes dataset introduced in Section \ref{sec:running_example} was new to them, and they were unsure which techniques would be the most appropriate. So, they asked their technologists to implement two new techniques: Odds Ratio and Relative Risk.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{infuse/usecase1b}
\caption{
The clinical researchers found an interesting pattern among
the glyphs indicating non-overlap of feature selection algorithm results.
These features were highly ranked by 2 of the 4 feature algorithms,
and unranked by the other 2, resulting in glyphs that resemble half-circles.
}
\label{fig:usecase1}
\end{figure}

>>>>

\begin{figure*}[ht]
\centering
\resizebox{0.9\linewidth}{!}{%
\begin{tikzpicture}
\newcommand*{\imgwidth}{3.7cm}
\newcommand*{\boxsize}{0.437cm}
\newcommand*{\boxpos}{(.295, -.18)}
\newcommand*{\rightimagepos}{(4.8, 0)}
\newcommand*{\leftimagepos}{(0, 0)}
\node[inner sep=0pt] at \leftimagepos
    {\includegraphics[width=\imgwidth]{infuse/ap}};
\node[inner sep=0pt] at \leftimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/ap}}};
\node[inner sep=2.5pt,very thick, text height=\boxsize] (zoom)
at \boxpos
    {\hspace*{\boxsize}};
\node[inner sep=-0.05pt] (lasso) at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\draw (zoom.north west) -- (lasso.north west);
\draw (zoom.south west) -- (lasso.south west);
\draw (zoom.north east) -- (lasso.north east);
\draw (zoom.south east) -- (lasso.south east);
\node[very thick, draw=red!90, text height=\boxsize]
at \boxpos {\hspace*{\boxsize}};
\node[inner sep=0pt, very thick] at \rightimagepos
    {\includegraphics[width=\imgwidth]{infuse/lasso}};
\node[inner sep=0pt, very thick, draw=red!90] at \rightimagepos
    {\phantom{\includegraphics[width=\imgwidth]{infuse/lasso}}};
\end{tikzpicture}%
}
\caption[The scatter-plot view allows users to compare multiple types of rankings.]{
The scatter-plot view allows users to compare multiple types of rankings.  In the case study, users became curious of the medication features that were chosen by only half of the models.  When reviewing these medications with domain experts, it became clear that features picked by the upper-half algorithms were as clinically significant as those picked by the bottom-half.  This indicates that merging results from feature selection algorithms makes sense for this predictive model.
}
\label{fig:usecase2}
\end{figure*}

\subsection{Insight 1: Data issues}
When the clinical researchers learned of \infuse's capabilities
to compare multiple feature selection algorithms, they decided to
expand their pipeline's feature selection algorithms from 2 to 4.
The team has used Information Gain and Fisher Score extensively
in prior work, and typically uses these same techniques due
to their familiarity and past success.
Nonetheless, the diabetes data set introduced in Section \ref{sec:running_example} was new to them, and they were unsure which techniques would be the most appropriate. So, they asked their technologists to implement two new techniques: Odds Ratio and Relative Risk.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{infuse/usecase1b}
\caption[The clinical researchers found an interesting pattern among
the glyphs.]{
The clinical researchers found an interesting pattern among
the glyphs indicating non-overlap of feature selection algorithm results.
These features were highly ranked by 2 of the 4 feature algorithms,
and unranked by the other 2, resulting in glyphs that resemble half-circles.
}
\label{fig:usecase1}
\end{figure}

### 2018-04-03 prospector/introduction.tex
restructure
fix figures and some citations

\section{Introduction}

@@

Data scientists often turn to machine learning, where the goal is to create predictive models based on information automatically learned from data with ground truth.  However, these machine learning techniques are often black-boxes and may be selected based only on performance metrics such as high accuracy scores, and not necessarily based on the interpretability and actionable insights of the model.  There has recently been a variety of techniques to inject humans-in-the-loop when building predictive models based on machine learning, from interactive training \cite{export:241307} to interactive feature selection \cite{infuse}.  However, interactive systems to effectively assess and evaluate the interpretability and actionable insights of a predictive model that go beyond simple accuracy metrics is still lacking.  We believe bringing humans into the loop at this stage can possibly lead to better models and consequently improved outcomes when the models are deployed.

>>>>

% \section{Introduction}

@@

Data scientists often turn to machine learning, where the goal is to create predictive models based on information automatically learned from data with ground truth.  However, these machine learning techniques are often black-boxes and may be selected based only on performance metrics such as high accuracy scores, and not necessarily based on the interpretability and actionable insights of the model.  There has recently been a variety of techniques to inject humans-in-the-loop when building predictive models based on machine learning, from interactive training \cite{amershi15} to interactive feature selection \cite{infuse}.  However, interactive systems to effectively assess and evaluate the interpretability and actionable insights of a predictive model that go beyond simple accuracy metrics is still lacking.  We believe bringing humans into the loop at this stage can possibly lead to better models and consequently improved outcomes when the models are deployed.

### 2018-04-03 prospector/related_work.tex
fix figures and some citations

Having access to the internals of a machine learning algorithm also allows direct interaction with the models and to improve them on the fly.
BaobabView (van den Elzen and van Wijk~\cite{6102453}) offers interactive decision tree construction.
Steed~\etal~\cite{5332586,doi:10.1559/152304009788988314}
guides regression model creation by enhancing interaction
with the input data.
EnsembleMatrix (Talbot~\etal~\cite{Talbot:2009:EIV:1518701.1518895})
allows users to combine already computed classification models to
build ensemble models.
Some recent interactive machine learning tools \cite{
export:241307,
Amershi:2011:DEE:2046396.2046416,
Amershi:2012:RIM:2207676.2207680,
Amershi:2011:CHF:1978942.1978966,
Kapoor:2010:IOS:1753326.1753529,
kim2015scalable,
Leung2014710,
Mishra:2015:SAI:2700171.2791022,
export:141330})
are more algorithm agnostic, but depend on general
performance measures like confusion matrices,
area under ROC curve (AUC) measures,
result distribution of data points, and
feature weights according to model independent statistics.

@@

Cortez and Embrechts~\cite{cortez11,Cortez20131} and Kim~\etal~\cite{kim2014bayesian}
use sensitivity analysis to analyze and compare machine learning models of different algorithms.
Sensitivity analysis is similar to partial dependence except that it uses a few
base vectors (usually the mean, median, or quartiles of all observed values)
instead of computing the probabilities over all input points.
This method is faster than partial dependence but may miss critical details
about the prediction function especially if the function is strongly non-linear.

>>>>

Having access to the internals of a machine learning algorithm also allows direct interaction with the models and to improve them on the fly.
BaobabView (van den Elzen and van Wijk~\cite{6102453}) offers interactive decision tree construction.
Steed~\etal~\cite{5332586,doi:10.1559/152304009788988314}
guides regression model creation by enhancing interaction
with the input data.
EnsembleMatrix (Talbot~\etal~\cite{Talbot:2009:EIV:1518701.1518895})
allows users to combine already computed classification models to
build ensemble models.
Some recent interactive machine learning tools \cite{
amershi15,
Amershi:2011:DEE:2046396.2046416,
Amershi:2012:RIM:2207676.2207680,
Amershi:2011:CHF:1978942.1978966,
Kapoor:2010:IOS:1753326.1753529,
kim2015scalable,
Leung2014710,
Mishra:2015:SAI:2700171.2791022,
export:141330})
are more algorithm agnostic, but depend on general
performance measures like confusion matrices,
area under ROC curve (AUC) measures,
result distribution of data points, and
feature weights according to model independent statistics.

@@

Cortez and Embrechts~\cite{cortez2011opening,Cortez20131} and Kim~\etal~\cite{kim2014bayesian}
use sensitivity analysis to analyze and compare machine learning models of different algorithms.
Sensitivity analysis is similar to partial dependence except that it uses a few
base vectors (usually the mean, median, or quartiles of all observed values)
instead of computing the probabilities over all input points.
This method is faster than partial dependence but may miss critical details
about the prediction function especially if the function is strongly non-linear.

### 2018-04-03 tex/introduction/machine_learning.tex
names and stuff
fix figures and some citations

\begin{figure}
\centering
\includegraphics[height=8em,valign=t]{tex/introduction/age.png}
\caption[Influence function for ``age" from a Generalized Additive Model.]{
An influence function for ``age" from a Generalized Additive Model \cite{Caruana:2015:IMH:2783258.2788613}.
}
\label{figs:age}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{tex/decisiontree}
    \caption[Example Decision Tree]{A possible decision tree for the Diabetes prediction example\footnotemark. Note, that the tree has interval checks to model the relationship between ``weight'' in \si{kg} and ``height'' in \si{m}.}
    \label{figs:dctree}
\end{figure}
\footnotetext{The decision tree or its parameters are \emph{not} based on data and serve only illustratory purposes.}

>>>>

\begin{figure}
\centering
\includegraphics[height=8em,valign=t]{tex/introduction/age.png}
\caption[Influence function for ``age" of a Generalized Additive Model.]{
An influence function for ``age" of a Generalized Additive Model \cite{Caruana:2015:IMH:2783258.2788613}.
}
\label{figs:age}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{tex/decisiontree}
    \caption[Example Decision Tree.]{A possible decision tree for the Diabetes prediction example\footnotemark. Note, that the tree has interval checks to model the relationship between ``weight'' in \si{kg} and ``height'' in \si{m}.}
    \label{figs:dctree}
\end{figure}
\footnotetext{The decision tree or its parameters are \emph{not} based on data and serve only illustratory purposes.}

### 2018-04-03 tex/introduction/motivation.tex
some citations
fix figures and some citations

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/emradio.png}
\caption{
The physical programmable circuit used by Bird and Layzell \cite{Bird:2002:ERI:1251972.1252349} for solving the task of automatically designing oscillators.
}
\label{figs:emradio}
\end{figure}
% https://people.duke.edu/~ng46/topics/evolved-radio.pdf

\par \noindent (3)
\todo{toaster example}
% \cite{2017arXiv171209665B}
% https://arxiv.org/pdf/1712.09665.pdf

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/adversarialtoaster.png}
\caption{
\todo{TODO}
}
\label{figs:toaster}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/emradio.png}
\caption[Programmable circuit to automatically design oscillators.]{
The physical programmable circuit used by Bird and Layzell \cite{Bird:2002:ERI:1251972.1252349} for solving the task of automatically designing oscillators.
}
\label{figs:emradio}
\end{figure}
% https://people.duke.edu/~ng46/topics/evolved-radio.pdf

\par \noindent (3)
\todo{toaster example}
% \cite{2017arXiv171209665B}
% https://arxiv.org/pdf/1712.09665.pdf
% https://arxiv.org/abs/1712.09665

\begin{figure}
\centering
\includegraphics[height=10em]{tex/introduction/adversarialtoaster.png}
\caption[The adversarial patch.]{
The adversarial patch. When put on any image, the image will get classified as toaster.
}
\label{figs:toaster}
\end{figure}
